### 2022-09-19 README.Rmd
README updated

# melt - Multiple Empirical Likelihood Tests
<!-- badges: start -->
[![Project Status: Active - The project has reached a stable, usable state and is being actively developed.](https://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/#active)
[![CRAN status](https://www.r-pkg.org/badges/version/melt)](https://CRAN.R-project.org/package=melt)
[![R-CMD-check](https://github.com/markean/melt/actions/workflows/check-standard.yaml/badge.svg)](https://github.com/markean/melt/actions/workflows/check-standard.yaml)
[![Codecov test coverage](https://codecov.io/gh/markean/melt/branch/master/graph/badge.svg)](https://app.codecov.io/gh/markean/melt?branch=master)
<!-- badges: end -->

@@

* `el_lm()` fits a linear model with empirical likelihood.
* `el_glm()` fits a generalized linear model with empirical likelihood.
* `confint()` computes confidence intervals for model parameters.
* `confreg()` computes a confidence region for model parameters.
* `elt()` tests a linear hypothesis.
* `elmt()` performs multiple testing simultaneously.

>>>>

# melt - Multiple Empirical Likelihood Tests <a href="https://markean.github.io/melt/"><img src="man/figures/logo.png" align="right" height="139" /></a>

<!-- badges: start -->
[![Project Status: Active - The project has reached a stable, usable state and is being actively developed.](https://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/#active)
[![CRAN status](https://www.r-pkg.org/badges/version/melt)](https://CRAN.R-project.org/package=melt)
[![R-CMD-check](https://github.com/markean/melt/actions/workflows/check-standard.yaml/badge.svg)](https://github.com/markean/melt/actions/workflows/check-standard.yaml)
[![Codecov test coverage](https://codecov.io/gh/markean/melt/branch/master/graph/badge.svg)](https://app.codecov.io/gh/markean/melt?branch=master)
<!-- badges: end -->

@@

* `el_lm()` fits a linear model with empirical likelihood.
* `el_glm()` fits a generalized linear model with empirical likelihood.
* `confint()` computes confidence intervals for model parameters.
* `confreg()` computes confidence region for model parameters.
* `elt()` tests a linear hypothesis.
* `elmt()` performs multiple testing simultaneously.
